Dynamics Analysis: The Sound of Teaching Music 1

### 2020-12-03 experiment-1/analysis/preprocessor/included_summary.Rmd
move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Workflow
1. filter with `filtering.R`
2. check the details of errors and remove some participants if needed (`error_summary.Rmd`)
3. trim data (i.e., remove outliers) with `trimming.R`
4. check trimmed data and remove some participants if needed (**this script**: `included_summary.Rmd`)

@@

### Key Velocity (Individual)
```{r vel-summary, echo = FALSE}
dt_vel[SubNr != 1, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Condition, Skill, Subcomponent)]
```

@@

### KV Difference (Individual)
```{r vel-diff-summary, echo = FALSE}
dt_vel_diff[SubNr != 1, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, Subcomponent)]
```

>>>>

# Workflow
1. filter with `filtering.R`
2. check the details of errors and remove some participants if needed (`error_summary.Rmd`)
3. trim data (i.e., remove outliers) with `trimming_ioi.R`, `trimming_kot.R`, `trimming_vel.R`
4. check trimmed data and remove some participants if needed (**this script**: `included_summary.Rmd`)

@@

### Key Velocity (Summary)
```{r vel-summary, echo = FALSE}
dt_vel[SubNr != 1, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Condition, Skill, Subcomponent)]
```

@@

### KV Difference (Summary)
```{r vel-diff-summary, echo = FALSE}
dt_vel_diff[SubNr != 1, .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, Subcomponent)]
```

### 2020-12-03 experiment-1/analysis/stats/dynamics.Rmd
move stuff to experiment-1
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Dynamics Analysis: The Sound of Teaching Music 2'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

2. Excluded participants
- SubNr 3: Insufficient motor skills

@@

ggline(vel_dyn_seq, x = "RowNr", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Note", ylab = "", title = "KV: Dynamics") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,72,1))

@@

ggline(vel_diff_dyn_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "", title = "KV-Diff: Dynamics") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,71,1))
```

@@

ggline(vel_art_seq, x = "RowNr", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Note", ylab = "", title = "KV: Articulation") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,72,1))

@@

ggline(vel_diff_art_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "", title = "KV-Diff: Articulation") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,71,1))
```

>>>>

---
title: 'Dynamics Analysis: The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

2. Excluded participants

- SubNr 1: Most of responses (more than 90%) were removed due to outliers
- SubNr 3: Experimental error
- SubNr 8: Experimental error
- SubNr 14: Experimental error
- SubNr 16: A deviated tempo

@@

ggline(vel_dyn_seq, x = "RowNr", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Note", ylab = "", title = "KV: Dynamics") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,67,1))

@@

ggline(vel_diff_dyn_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "", title = "KV-Diff: Dynamics") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,66,1))
```

@@

ggline(vel_art_seq, x = "RowNr", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Note", ylab = "", title = "KV: Articulation") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,67,1))

@@

ggline(vel_diff_art_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "", title = "KV-Diff: Articulation") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,66,1))
```
